---
title: "CO1 RMD"
author: "Owen W"
date: "2/16/2022"
output: html_document
---
```{r}
summary(iris)
```

```{r}
2+2

mean(iris$Sepal.Length)
```

Two plus two equals `r 2+2`.

# Basics

## Text

Plain text - hello!
Add two spaces to start a new paragraph.  
*italics* and _italics_
**bold** and __bold__
superscript^2^
~~strikethrough~~
[link](www.rstudio.com)

## Headers (level 2)
```{r,eval=FALSE}
Make sure to leave a space between the # and your text
#Header 1
## Header 2
```
### Header 3
#### Header 4
##### Header 5
###### Header 6

## Symbols
endash: --
emdash: ---
ellipsis: ...
inline equation: $A= pi*r^(2)$

horizontal rule(or slide break):

***

## Formatting

>block quote

* unordered list
*item 2
  + sub-item 1 (one tab)
  + sub-item 2 (one tab)
  
1. ordered list
2. item 2
    + sub-item 1 (two tabs)
    + sub-item 2 (two tabs)
    
First Header | Second Header
-------------|--------------
Table `r mean(Sepal.Length)` | Cell 2
Cell 3 | Cell 4

## Date
```{r}
#Add this to date so that today's date is printed whenever doc knitted
title: "Rmarkdown_Intro"
author: "Owen W"
date: "`r Sys.Date()`"
```

>Most of this information was taken from this useful
[cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

# Code Specifications

## Displays Code
```{r,echo=FALSE,eval=FALSE}
echo=TRUE: Whether to display code along with results
Default is echo=TRUE
```
```{r, echo=FALSE}
summary(iris)
```
## Display Warnings
```{r, warning=FALSE,eval=FALSE}
warning=TRUE: Whether to display warnings
```

### With Warning
```{r, warning=TRUE}
data <- data.frame(x = 1.5,
                   y = 1.5)
ggp <- ggplot(data, aes(x, y)) +
  geom_point()

ggp +
  scale_x_continuous(limits = c(2, 5))
```

