---
title: Data IO
author: R package build
date: '2022-02-23'
slug: data-io
categories: []
tags: []
---
```{r}
library(tidyverse)
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "df.csv")
```
```{r}
read_csv("df.csv")
```
```{r}
url<-'https://raw.githubusercontent.com/welcho2020/tidyverse/main/edibnb-badnames.csv'
edibnb_badnames <- read_csv(url)
names(edibnb_badnames)
```
# R doesn't allow spaces in variable names
## Option 1 Define Columns
```{r}
edibnb_col_names <- read_csv(url,
                             col_names = c("id", "price", 
                                           "neighbourhood", "accommodates",
                                           "bathroom", "bedroom", 
                                           "bed", "review_scores_rating", 
                                           "n_reviews", "url"))
names(edibnb_col_names)
```
## Option 2 - Format text to snake_case
```{r}
edibnb_clean_names <- read_csv(url) %>%
  janitor::clean_names()
names(edibnb_clean_names)
```
# Variable types
```{r}
df_na <- 'https://raw.githubusercontent.com/welcho2020/tidyverse/main/df-na.csv'
read_csv(df_na)
```
## Option 1. Explicit NAs
```{r}
read_csv(df_na, 
         na = c("", "NA", ".", "9999", "Not applicable"))
```
## Option 2. Specify column types
```{r}
read_csv(df_na, col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```
# Column types
##type function	data type
##col_character()	character
##col_date()	date
##col_datetime()	POSIXct (date-time)
##col_double()	double (numeric)
##col_factor()	factor
##col_guess()	let readr guess (default)
##col_integer()	integer
##col_logical()	logical
##col_number()	numbers mixed with non-number characters
##col_numeric()	double or integer
##col_skip()	do not read
##col_time()	time

#Case study: Favourite foods
```{r}
library(tidyverse)
library(readxl)
```


```{r}
library(readxl)
fav_food <- read_excel("/Users/owenwelch/Desktop/website1/favourite-food.xlsx")
fav_food
```

## Variable names

```{r}
fav_food <- read_excel("/Users/owenwelch/Desktop/website1/favourite-food.xlsx") %>%
  janitor::clean_names()
fav_food
```

## Handling NAs
```{r}
fav_food <- read_excel("/Users/owenwelch/Desktop/website1/favourite-food.xlsx",
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
```
## Make age numeric
```{r}

fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)
```
## Socio-economic status
```{r}
fav_food %>%
  count(ses)
```
## Make ses factor
```{r}
fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```
## Putting it altogether
```{r}
fav_food <- read_excel("/Users/owenwelch/Desktop/website1/favourite-food.xlsx", na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food
```
## Out and back in
```{r}
write_csv(fav_food, file = "/Users/owenwelch/Desktop/website1/favourite-food.xlsx")
fav_food_clean <- read_csv("/Users/owenwelch/Desktop/website1/favourite-food.xlsx")
```

## read_rds() and write_rds()
###read_rds(path), write_rds(x, path)

## Out and back in, take 2
```{r}
write_rds(fav_food, file = "/Users/owenwelch/Desktop/website1/favourite-food.xlsx")
fav_food_clean <- read_rds("/Users/owenwelch/Desktop/website1/favourite-food.xlsx")
fav_food_clean %>%
  count(ses)
```
## Other types of data
###googlesheets4: Google Sheets
###haven: SPSS, Stata, and SAS files
###DBI, along with a database specific backend (e.g. RMySQL, RSQLite, RPostgreSQL etc): allows you to run SQL queries against a database and return a data frame
###jsonline: JSON
###xml2: xml
###rvest: web scraping
###httr: web APIs
###sparklyr: data loaded into spark
